---
output: github_document
---

[![Travis-CI Build Status](https://travis-ci.org/AustralianAntarcticDataCentre/raadsync.svg?branch=master)](https://travis-ci.org/AustralianAntarcticDataCentre/raadsync)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```



An R package for maintaining a library of satellite-derived and similar environmental data.

See [RAADTools](https://github.com/AustralianAntarcticDivision/raadtools) for reading, plotting, and manipulating these data.

## Installing

```{r,eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("AustralianAntarcticDataCentre/raadsync")
```

## Configuration files

Configuration files are used to tell `raadsync` which data sets to synchronise, along with settings such as the location of the data directory. A default configuration file is provided as part of the package:

```{r,eval=FALSE}
system.file("extdata", "raad_repo_config.json", package = "raadsync")
```

You will need to modify this configuration to suit your purposes (in particular, the default configuration sets `do_sync` to FALSE for all datasets, so it won't actually synchronise any data until you override one or more of these).

There are two different ways to manage configurations:

### 1. Default

Use the default configuration with local adjustments (recommended if you intend to mostly use datasets already defined in the default file). Create a local configuration file that alters or adds to the default configuration. Start with the example local configuration file provided in the package:

```{r,eval=FALSE}
file.copy(system.file("extdata","sample_local_config.json", package = "raadsync"),
          "/path/to/your/local_config.json")
```

Edit `/path/to/your/local_config.json` to suit your needs.

Then to use this configuration in combination with the default configuration file:

```{r,eval=FALSE}
cf = read_repo_config("/path/to/your/local_config.json")
sync_repo(cf)
```


### 2. Custom

Use your own configuration file entirely. You can use the default configuration file as a starting point.

  When using solely your own configuration file, specify NULL for the `default_config_file` parameter in `read_repo_config`:

```{r,eval=FALSE}
cf = read_repo_config("/path/to/your/config.json", NULL)
sync_repo(cf)
```
